---
output:
  revealjs::revealjs_presentation:
    self_contained: false
    transition: fade
    css: styles.css
    theme: serif
    reveal_options:
      slideNumber: true
    keep_md: yes
---




```{r  include=FALSE}
require(xtable, quietly = TRUE, warn.conflicts = T)
require(gridExtra, quietly = TRUE, warn.conflicts = T)
require(ggplot2, quietly = TRUE, warn.conflicts = T)
require(tables, quietly = TRUE, warn.conflicts = T)
require(knitr, quietly = TRUE, warn.conflicts = T)
require(dplyr, quietly = TRUE, warn.conflicts = T)
require(reshape2, quietly = TRUE, warn.conflicts = T)

load(file = "C:\\Data\\RData\\adol2web.Rdata")
load(file = "C:\\Data\\RData\\adol2CSAweb.Rdata")
load(file = "C:\\Data\\RData\\set.Rdata")
load(file = "C:\\Data\\RData\\setCSA.Rdata")

source(file="C:\\Abel\\WebData2016\\WebdataFunctions.R")

```


##ASI Web Data
Total Number of Questionnaires
All Sites AASI-1 through 3 
Updated April 2016 

```{r fig.width=5, fig.height=4, echo=FALSE,  results='asis',dev='png' }
block1<-data.frame(x=c("Adult Males", "Adult Females", "Adolescent Males", "Adolescent Females", "Total"), y=rep(0,5))
colnames(block1)<-c("Questionnaire Type", "Count")
block1[1,2] <- ifelse(dim(set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n))[1]==0,0, set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n) )
block1[2,2] <- ifelse(dim(set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n))[1]==0,0, set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n) )
block1[3,2] <- ifelse(dim(adol %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n))[1]==0,0, adol %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n) )
block1[4,2] <- ifelse(dim(adol %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n))[1]==0,0, adol %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n) )
block1[5,2] <- sum(block1[1:4,2])
kable(block1, format = "html",   pad=0, format.args =  list(big.mark = ','))
```
-----




## <small>Adult - Gender 

```{r echo=FALSE,  results='asis' }
block2<-data.frame(t(rep(0,4)))
colnames(block2)<-c("Male Counts", "Male Percent", "Female Counts", "Female Percent")
block2[1,1]<-block1[1,2]
block2[1,3]<-block1[2,2]
block2[1,2]<-block2[1,1]/(block2[1,1]+block2[1,3])
block2[1,4]<-block2[1,3]/(block2[1,1]+block2[1,3])
block2[1,1]<-formatC(block2[1,1], format="d", big.mark=',')
block2[1,3]<-formatC(block2[1,3], format="d", big.mark=',')
block2[1,2]<-sprintf("%1.1f%%", block2[1,2]*100)
block2[1,4]<-sprintf("%1.1f%%", block2[1,4]*100)
kable(block2, format = "html", align='r',   pad=0)
```


```{r fig.width=6, fig.height=4, echo=FALSE,  dev='svg'}
block3<-data.frame(x1=c("Males", "Females"), res=rep(0,2))
block3[1,2] <- ifelse(dim(set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n))[1]==0,0, set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n) )
block3[2,2] <- ifelse(dim(set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n))[1]==0,0, set  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n) )

g <- ggpie(block3, "", by = "x1", totals ="res")
g

```
</small>



## <small>Adult - Age</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="acat", newvn="Age")
#kable(tub[[2]], format = "html",  alaign="r",   pad=0, row.names = NA)
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.75, echo=FALSE, dev='svg' }
tub[[3]]
```


## <small>Adult - Race</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="race", newvn="Race")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```


## <small>Adult - Marital Status</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="marital", newvn="Marital Status")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```

## <small>Adult - Religion</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="religion", newvn="Religion")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>


## <small>Adult - Education</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="educ", newvn="Education")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```

## <small>Adult - Income</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="income", newvn="Income")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>

## <small>Adult - Victimization</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="vic73", newvn="Victimization")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```
</small>



## <small>Adult - Sexual Orientation - Kinsey Scale</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=set, varr="sexpref", newvn="Sexual Orientation")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
dat<-tub[[1]]
dat$xx<-dat$"Sexual Orientation"
#dat$Sexual_Orientation <- gsub("Heterosexual", "Het", dat$Sexual_Orientation)
#dat$Sexual_Orientation <- gsub("Homosexual", "Hom", dat$Sexual_Orientation)
#kable(dat, format = "html",   pad=0, row.names = NA)
g1<-ggplot(dat, aes(x = xx, y = perc, fill=sex)) +    geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  xlab("Sexual Orientation")  + theme_minimal() +  
	geom_text(aes(y=perc, ymax=perc, label=perclab  ), position= position_dodge(width=0.9), vjust=-.5, color="black", size = 3) +
	scale_y_continuous("Percent",limits=c(0,max(dat$perc)*1.1))  + theme(axis.text=element_text(size=8))
g1
```
</small>

## <small>Adult - Problematic Sexual Behaviors Group 1
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c('childmol', 'childporn', 'childmeet')
labs<-c("Child Molestation", "Child Pornography", "Child Contact")
out2<-PercBox1(vars=vars,labs=labs,data=set)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
```
<left><small>NOTE 1: Child Pornography is the use of pornography of minors.     
NOTE 2: Child Contact is the communicating with or meeting for sexual purposes.     
NOTE 3: Child Contact and Child Pornography counts are smaller because these behaviors were introduced in the AASI-3.  
</small></small></left>
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs) , y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent")  +  xlab("Behavior")  + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```


## <small>Adult - Problematic Sexual Behaviors Group 2
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c('rape', 'frottage', 'obsphone')
labs<-c("Rape", "Frottage", "Obscene Calls/Texts")
out2<-PercBox1(vars=vars,labs=labs,data=set)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>

## <small>Adult - Problematic Sexual Behaviors Group 3
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c('expose', 'publmast', 'voyeur')
labs<-c("Public Exposure", "Public Masturbation", "Voyeurism")
out2<-PercBox1(vars=vars,labs=labs,data=set)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>




## <small>Adult - Problematic Sexual Behaviors Group 4
```{r fig.width=7, fig.height=3.5, echo=FALSE,  results='asis',dev='svg' }
vars<-c('bestial', 'copraph', 'sadism', 'masochsm', 'fetish', 'transvst')
labs<-c('Bestiality', 'Copraphilia', 'Sadism', 'Masochism', 'Fetishism', 'Transvestism')
out2<-PercBox1(vars=vars,labs=labs,data=set)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>


## <small>Adult - Problematic Sexual Behaviors Group 5
```{r fig.width=7, fig.height=3.5, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'porn','prostitu', 'internet', 'phonesex', 'affairs', 'affstran')
labs<-c( 'Pornography','Prostitution', 'Internet Sex', 'Phone Sex', 'Affairs', 'Affairs \nw/Strangers')
out2<-PercBox1(vars=vars,labs=labs,data=set)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
```
<small>
NOTE 1: Prostitution is the use of prostitutes.         
NOTE 2: Internet Sex is the use of the internet for sexual purpose.
</small></small>
```{r fig.width=7, fig.height=3.0, echo=FALSE,  results='asis',dev='svg' }  
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black", size =2.5) +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```




## <small>Adult - Child Sexual Abusers 
Onset, End, # of Children and # of Times
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
labs<-c("Age First \nTouched Child", "Age Last \nTouched Child", "# of Children \nTouched", "# of Times - \nLifetime")
vars<-c("v5a","v5b","v5c","v5d")
out2<-MeanBox1(vars=vars, labs=labs, data=setcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)

out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=round(value,1)), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Mean",limits=c(0,max(out3$value)*1.1))
g1
```
</small>



## <small>Adult - Child Sexual Abusers - Amount of Force Used

```{r fig.width=7, fig.height=3.5, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'v5f1','v5f2', 'v5f3', 'v5f4', 'v5f5', 'v5f6')
labs<-c( 'Started by \nChild','Mutual \nAgreement', 'Verbal \nThreat', 'Physical \nRestraint', 'Excessive \nAggression', 'Death')
out2<-PercBox1(vars=vars,labs=labs,data=setcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)

out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black", size =3) +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>




## <small>Adult - Child Sexual Abusers - Gender and Age of Victims
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'bu14','bo13', 'gu14', 'go13')
labs<-c( 'Boys under 14','Boys 14-17', 'Girls under 14', 'Girls 14-17')
out2<-PercBox1(vars=vars,labs=labs,data=setcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)

out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(set$sex)[1]==0 & table(set$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(set$sex)[1]>0 & table(set$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black", size =3) +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>



## <small>Adult - Child Sexual Abusers - Relationship to Victims
```{r   echo=FALSE,  results='asis'  }
vars<-c( 'v5i1','v5i2','v5i3','v5i4','v5i5','v5i6','v5i7','v5i8','v5i9','v5i10','v5i11','v5i12','v5i13','v5i14')
labs<-c('Biological Children', 'Stepchildren or Children of Live-in Partner', 'Foster Children', 'Adopted Children', 'Grandchildren',
	'Younger Brothers & Sisters', 'Nieces & Nephews', 'Children of Neighbors or Other Acquaintances', 'Children Left in My Care by Organization',
	'Strangers', 'Children Who I Teach', 'Children Who I coach or Train', 'Children Who Are Patients or Clients', 
	'Children Who I Connect with in a Religious Context')
out2<-PercBox1(vars=vars,labs=labs,data=setcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
```
</small>









## <small>Adolescent - Gender 

```{r echo=FALSE,  results='asis' }
block2<-data.frame(t(rep(0,4)))
colnames(block2)<-c("Male Counts", "Male Percent", "Female Counts", "Female Percent")
block2[1,1]<-block1[3,2]
block2[1,3]<-block1[4,2]
block2[1,2]<-block2[1,1]/(block2[1,1]+block2[1,3])
block2[1,4]<-block2[1,3]/(block2[1,1]+block2[1,3])
block2[1,1]<-formatC(block2[1,1], format="d", big.mark=',')
block2[1,3]<-formatC(block2[1,3], format="d", big.mark=',')
block2[1,2]<-sprintf("%1.1f%%", block2[1,2]*100)
block2[1,4]<-sprintf("%1.1f%%", block2[1,4]*100)
kable(block2, format = "html",   pad=0)
```


```{r fig.width=6, fig.height=4, echo=FALSE,  dev='svg'}
block3<-data.frame(x1=c("Males", "Females"), res=rep(0,2))
block3[1,2] <- ifelse(dim(adol  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n))[1]==0,0, adol  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Male")   %>% select(n) )
block3[2,2] <- ifelse(dim(adol  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n))[1]==0,0, adol  %>% group_by(sex) %>% summarize(n=n()) %>% filter(sex=="Female") %>% select(n) )

g <- ggpie(block3, "", by = "x1", totals ="res")
g

```
</small>





## <small>Adolescent - Age</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="age", newvn="Age")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```


## <small>Adolescent - Race</small>
<small>
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="race", newvn="Race")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```


## <small>Adolescent - Religion
```{r   echo=FALSE,  results='asis'  }
tub<-tabb(data=adol, varr="religion", newvn="Religion")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>


## <small>Adolescent - Education Level
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="educ", newvn="Education")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```



## <small>Adolescent - Repeated Grade
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="repgrade", newvn="Repeated Grade")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```



## <small>Adolescent - Special Education
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="spcleduc", newvn="Special Education")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```



## <small>Adolescent - Impregnated Girl/Times Pregnant
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="pregnant", newvn="Pregnant")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```




 

## <small>Adolescent - Number of Families Lived With
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="families", newvn="Families")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```




 


## <small>Adolescent - Times Raped
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="tmsraped", newvn="Times Raped")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```




## <small>Adolescent - Sexual Orientation
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="homohetr", newvn="Orientation")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```


## <small>Adolescent - Accused
```{r fig.width=10, fig.height=9, echo=FALSE,  results='asis',dev='png' }
vars<-c( 'accused1', 'accused2', 'accused3', 'accused4', 'accused5', 'accused6', 'accused7')
labs<-c( 'Never Blamed', 'Never Near the Kid', 'Was Near the Kid', 'The Kid Wanted Me To', 'Just Like They Said', 'Not As Much as They Said',
	'A Lot More Than They Know')
out2<-PercBox1(vars=vars,labs=labs,data=adol)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
```
</small>


## <small>Adolescent - Not Accused
```{r  echo=FALSE,  results='asis' }
tub<-tabb(data=adol, varr="naccused", newvn="Not Accused")
print(xtable(tub[[2]],align="llrrrr"  ),type="html",include.rownames=FALSE)
```
</small>
```{r fig.width=7, fig.height=3.0, echo=FALSE, dev='svg' }
tub[[3]]
```




## <small>Adolescent - Sexual Behaviors Group 1
```{r fig.width=7, fig.height=3.5, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'bhv1','bhv3', 'bhv4', 'bhv5', 'bhv7', 'bhv8')
labs<-c( 'Public \nExposure', 'Window \nPeeping', 'Sexual with \nAnimals', 'Obscene \nLetters/Calls', 'Child Sexual \nAbuse', 'Frottage')
out2<-PercBox1(vars=vars, labs=labs, data=adol)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(adol$sex)[1]==0 & table(adol$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black", size=2.5) +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>





## <small>Adolescent - Sexual Behaviors Group 2
```{r fig.width=7, fig.height=3.5, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'bhv2','bhv6', 'bhv9', 'bhv10', 'bhv11', 'bhv12', 'bhvint')
labs<-c( 'Fetishism', 'Masochism', 'Tranvestism', 'Sadism', 'Telephone Sex', 'Used Erotica', 'Internet Sex')
out2<-PercBox1(vars=vars, labs=labs, data=adol)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(adol$sex)[1]==0 & table(adol$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black", size=2.5) +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))  + theme(axis.text=element_text(size=8))
g1
```
</small>



## <small>Adolescent - Child Sexual Abusers
Onset, End, # of Children and # of Times
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c("bhv7a","bhv7b","bhv7c","bhv7d")
labs<-c("Age First \nTouched Child", "Age Last \nTouched Child", "# of Children \nTouched", "# of Times - \nLifetime")
out2<-MeanBox1(vars=vars, labs=labs, data=adolcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)

out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(adol$sex)[1]==0 & table(adol$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=round(value,1)), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Mean",limits=c(0,max(out3$value)*1.1))
g1
```
</small>






## <small>Adolescent - Child Sexual Abusers - Amount of Force Used
```{r   echo=FALSE,  results='asis'  }
vars<-c( 'bhv7e1', 'bhv7e2' , 'bhv7e3', 'bhv7e4', 'bhv7e5', 'bhv7e6', 'bhv7e7', 'bhv7e8')
labs<-c( 'Initiated by Child', 'Mutual Consent', 'Promised Toy', 'Tricked Kid', 'Verbal Threat', 'Physical Restraint', 'Physical Aggression', 'Death of Child')
out2<-PercBox1(vars=vars,labs=labs,data=adolcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
```
</small>


## <small>Adolescent - Child Sexual Abusers - Age & Gender
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'bhv7f1', 'bhv7f2' , 'bhv7f3', 'bhv7f4')
labs<-c( 'Girls 3-4 \nYrs Younger', 'Boys 3-4 \nYrs Younger', 'Girls 5+ \nYrs Younger', 'Boys 5+ \nYrs Younger')
out2<-PercBox1(vars=vars,labs=labs,data=adolcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(adol$sex)[1]==0 & table(adol$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1)) + theme(axis.text=element_text(size=10))
g1
```
</small>






## <small>Adolescent - Child Sexual Abusers - Relationship to Victims
```{r fig.width=7, fig.height=4, echo=FALSE,  results='asis',dev='svg' }
vars<-c( 'bhv7g1', 'bhv7g2' , 'bhv7g3', 'bhv7g4')
labs<-c( 'Younger Sibling', 'Foster Sibling', 'Other Family', 'Non-Family')
out2<-PercBox1(vars=vars,labs=labs,data=adolcsa)
print(xtable(out2[[1]],align="llrrrr"),type="html",include.rownames=FALSE)
out2a<-data.frame(out2[[2]])
out2a$beh <-labs
  if ( table(adol$sex)[1]==0 & table(adol$sex)[2] >0 ) {colnames(out2a)<- c("Male",  "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] ==0 ) {colnames(out2a)<- c("Female", "Behavior")}
  if ( table(adol$sex)[1]>0 & table(adol$sex)[2] >0 )  {colnames(out2a)<- c("Male", "Female", "Behavior")}
out3<-melt(out2a, id="Behavior")
g1<-ggplot(out3, aes(x = factor(Behavior, levels=labs), y = value, fill=variable)) +   geom_bar(stat = "identity", position="dodge") +
 	scale_fill_manual(values=c("lightslateblue", "Navyblue"), name="Gender") +  ylab("Percent") +  xlab("Behavior") + theme_minimal() +  
	geom_text(aes(y=value, ymax=value, label=paste0(round(value,1),"%"  )), position= position_dodge(width=0.9), vjust=-.5, color="black") +
	scale_y_continuous("Percent",limits=c(0,max(out3$value)*1.1))
g1
```
</small>